### 2021-05-05 papers/jin-thesis/Chapters/1Introduction.tex
Thesis edits

	Neurodegenerative diseases, such as Alzheimer's or Huntinton's disease, are a leading cause of death in the United States \cite{eschbach2011cytoplasmic}. Scientists have yet to find a prevention or cure to these fatal diseases but suggests that motor protein failure directly contributes to cell degeneration. More specifically, defects in the motor protein dynein have been linked to neurodegeneration due to the cell's funtional dependence on dynein and its mechanical properties. However, dynein possesses a unique structure causing it to stochasitcally move around the cell and be unpredictable in nature. Thus, fully understanding the mechanisms of dynein can allow us to further understand causes of its failure. In this paper, we propose a model of dynein that uses Monte Carlo methods and a Brownian dynamics simulation to reproduce dynein's unique steping behavior. What follows is a brief introduction to the dynein motor protein, a review of the powerstroke model, and the framework for a computational simulation of the powerstroke, which seeks to replicate an inter head stepping correlation observed by experimentalist Ahmet Yildiz \textit{et al.} \cite{Dewitt2012}.

@@

Cells are complicated. They are the fundamental unit of life and have the ability to move, perfectly divide, and spatially organize themselves. When these functions fail, cell degeneration can cause fatal diseases within their host. Their functionality entirely depends on two-legged molecular proteins, named \textit{motor proteins}, that carry information along a microtubule track. These microtubules form the cytoskeleton in the cell and act as a walkway for the proteins (see Figure (\ref{fig:ArtDynein})). These motor proteins are myosin, kinesin, and dynein and are shown below in Figure (\ref{fig:Compare}). Because of kinesin and myosin's compact structure being close to the microtubule, their legs take turns alternating steps like a human and exhibit a uniform ``hand-over-hand" stepping pattern. On the contrary, dynein's structure involves two autonomous motors that cause inconsistent steps. As opposed to kinesin and myosin's uniform stepping, dynein exhibits an inchworm walk with one leg consistently ahead of the other, emulating a limping motion.

\begin{figure}[H]
	\centering
	\includegraphics[width=0.4\columnwidth]{Figures/motor_comparison.png}
	\caption[Motor Proteins]{\textbf{Motor Proteins} Structure of myosin, kinesin, and dynein. \cite{JohnsonArt}}
	\label{fig:Compare}
\end{figure}

In addition to their structural differences, dynein walks towards the negative end of the microtubule while its motor protein siblings walk towards the positive end. Because microtubules are protein dimers constructed from negatively charged $\alpha$- and positively charged $\beta$-tubulins, the microtubule track is polarized depending on which tubulin dominates at the end points. In a eukaryotic cell, microtubules typically stem outwards from the cell's nucleus to the cell walls where the $\beta$ tubulin is exposed, generating a negative end at the nucleus and influencing dynein's directionality. Figure (\ref{fig:transport}) displays kinesin and dynein experiencing a charged attraction to the end points, while they share a cargo to deliver information during axonal transport.

@@

Dynein's ``leg" is a complex protein assembly composed of linked amino acids subunits, called polypeptides, separated into three main domains. Figure (\ref{fig:structure}) displays these as the tail, the AAA+ rings (or motor), and the microtubule binding domain. The tail and the motor domains are connected by separate linkers, while the motor and the binding domains are connected by stalks. Both the linker and stalk measures greater than 20 nm in length, causing dynein to stand up to 50 nm high.

@@

Dynein's ability to step is entirely ATP driven under the process of ATP hydrolysis. The ATP binds onto the motor domain and converts chemical energy into mechanical energy for dynein to transition between different conformational states (physicial arrangements) during a step. This process allows the binding domains to unbind and reattach at different locations on the microtubule and thus, permit varying step sizes. To measure dynein's step, an axis is defined on the microtubule.

@@

While ATP hydrolysis dictates the forward stepping during dynein's walk, the geometry of the domains is still a question for experimentalists. How exactly do the motor, tail, and linker achieve processive motion? Do the motor domains act as knees and stretch out for a step? Or do the knees stay bent, while the tail swings forward? Despite ongoing debates, recent studies suggest the former and named this process the powerestroke model.

@@

Here, affinity refers to the tendency and strength of the domain binding to the microtubule - high affinity being a secure attachment to the microtubule, while low affinity is more relaxed. The cycle utilizes the conformational transitions between high and low affinity to explain dynein's unbinding and rebinding process. This transition is governed by the addition of an ATP unit, which loosens the ``foot" from the microtubule (steps 3 to 4), stretches the linker (steps 5 to 6), and tightens the ``foot" back onto the microtubule (steps 6 to 7), pulling the whole protein forward. This key detail within the transition of stretching the linker distinguishes a ``pre-" and a ``post-" stroke state during the powerstroke model and can be analogous to bending a knee upwards and kicking the foot forwards to stretch the knee and take a step. A closer visualization of this transition between pre- and post-stroke states can be seen in Figure (\ref{fig:Powerstroke}), where the linker is highlighted in yellow.

@@

Experimentalists measures dynein in various ways that utilizes electron microscopy and quantum measuring devices. Some attach quantum dots to dynein's motor domains, while others replace the tail with an artificial quantum rod. Despite the different procedures, all measuring techniques suffer from their inability to measure steps within $\sim 0.4$ nm of where the binding domain lifted off. This causes short step lengths, where the binding domain quickly rebinds after unbinding, to be undetectable. The various measuring procedures and experimental limitations leads to different results and unique findings when observing different variables. In this paper, we focus on the unique observation by Yildiz \textit{et al.} of a stepping correlation between the initial interhead separation and step length because of the results contradicting previously accepted theories of independent stepping.

@@

Due to dynein's large size and stochastic nature, dynein's step was previously hypothesized to be independent from the initial conformational before the step. However, in 2012, Yildiz \textit{et al.} observed a correlation between the initial on-axis separation and the step length, indicating a dependence on the interhead separation \cite{Dewitt2012}. This discovery challenged established views on dynein's stepping processivity and pose the question of whether there exists interhead coordination between the motor domains when stepping. Figure (\ref{fig:YildizCorrelation}) below displays this correlation with a linear regression, where an existing non-zero slope indicates a dependence between the step and the initial on-axis separation.

@@

We want to further investigate Yildiz's unique stepping correlation by creating a compuational simulation of dynein and analyze the specific conditions that are required to replicate their results. Currently, other simulations that model dynein's step exist, but all of them are used to investigate the ATP hydrolysis mechanism during the mechanochemical cycle. These simulations suffer from numerous assumptions made about the physical aspects of dynein's step. (\textit{Should reference a simulation here}) Some assume that dynein can step only in increments of 8nm or that the rebinding process is constrained to a certain time frame. These limitations make it impossible for their models to replicate mechanical phenomenon observed in dynein's stepping, such as Yildiz's correlation from above.

To bridge this gap, Roundy \textit{et al.} constructed a physical model of dynein that explores the molecular interactions between the domains of dynein and its aqueous environment. Instead of making assumptions about the physical mechanics of the step, Roundy's model neglects the chemistry of the ATP exchange and assumes the energy transfer from ATP is incorporated within the binding processes. Researchers John Waczak and Elliott Capek successfully incorporated this model under an angle-dependent Brownian dynamics simulation, where each domain experienced Brownian motion to mimic stochastic movement \cite{Capek2017, }. They were able to track dynein's precise movement along a walk and compare their stepping results to experiment. However, they also discovered that dynein spends less than 5\% of its total stepping time in the low affinity state where the dynein exhibits the actual stepping motion ($<1$ ms unbound while $>20$ ms bound). Because of this, their simulation suffered from immense computation time and lacked the ability to optimize model parameters for a better fit to experiment. For this work, we will use their simulation as a foundation but replace the dynamical bounded state with a Monte Carlo algorithm. This allows us to only simulate the stepping motion, as the Monte Carlo will initially test equilibrium configurations before the step. This new method will drastically shorten computation time and generate larger ensembles of statistics. We intend to use this model to reproduce experimental measures and help verify existing understandings concerning the properties of dynein’s stepping mechanism. More specifically, we want reproduce Yildiz's unique findings and investigate the stepping dependence on the interhead separation.

>>>>

	Neurodegenerative diseases, such as Alzheimer's or Huntinton's disease, are a leading cause of death in the United States \cite{gammon2014neurodegenerative}. Scientists have yet to find a prevention or cure to these fatal diseases but suggests that motor protein failure directly contributes to cell degeneration. More specifically, defects in the motor protein dynein have been linked to neurodegeneration due to the cell's funtional dependence on dynein and its mechanical properties \cite{eschbach2011cytoplasmic}. However, dynein possesses a unique structure causing it to stochasitcally move around the cell and be unpredictable in nature. Thus, fully understanding the mechanisms of dynein can allow us to further understand causes of its failure. In this paper, we propose a model of dynein that uses Monte Carlo methods and a Brownian dynamics simulation to reproduce dynein's unique steping behavior. What follows is a brief introduction to the dynein motor protein, a review of the powerstroke model, and the framework for a computational simulation of the powerstroke, which seeks to replicate an inter head stepping correlation observed by experimentalist Ahmet Yildiz \textit{et al.} \cite{Dewitt2012}.

@@

Cells are complicated. They are the fundamental unit of life and have the ability to move, perfectly divide, and spatially organize themselves. When these functions fail, cell degeneration can cause fatal diseases within their host. Their functionality entirely depends on two-legged molecular proteins, named \textit{motor proteins}, that carry information along a microtubule track. These microtubules form the cytoskeleton in the cell and act as a walkway for the proteins (see Figure (\ref{fig:ArtDynein})). These motor proteins are myosin, kinesin, and dynein and are shown below in Figure (\ref{fig:Compare}). Because of kinesin and myosin's compact structure being close to the microtubule, their legs take turns alternating steps like a human and exhibit a uniform ``hand-over-hand" stepping pattern \cite{fehr2008kinesin}. On the contrary, dynein's structure involves two autonomous motors that cause inconsistent steps. As opposed to kinesin and myosin's uniform stepping, dynein exhibits an inchworm walk with one leg consistently ahead of the other, emulating a limping motion.

\begin{figure}[H]
	\centering
	\includegraphics[width=0.4\columnwidth]{Figures/motor_comparison.png}
	\caption[Motor Proteins]{\textbf{Motor Proteins} Structure of myosin, kinesin, and dynein. \cite{RonArt}}
	\label{fig:Compare}
\end{figure}

In addition to their structural differences, dynein walks towards the negative end of the microtubule while its motor protein siblings walk towards the positive end. Because microtubules are protein dimers constructed from negatively charged $\alpha$- and positively charged $\beta$-tubulins, the microtubule track is polarized depending on which tubulin dominates at the end points. In a eukaryotic cell, microtubules typically stem outwards from the cell's nucleus to the cell walls where the $\beta$ tubulin is exposed, generating a negative end at the nucleus and influencing dynein's directionality \cite{paschal1987retrograde}. Figure (\ref{fig:transport}) displays kinesin and dynein experiencing a charged attraction to the end points, while they share a cargo to deliver information during axonal transport.

@@

Dynein's ``leg" is a complex protein assembly composed of linked amino acids subunits, called polypeptides, separated into three main domains \cite{Burgess2003}. Figure (\ref{fig:structure}) displays these as the tail, the AAA+ rings (or motor), and the microtubule binding domain. The tail and the motor domains are connected by separate linkers, while the motor and the binding domains are connected by stalks. Both the linker and stalk measures greater than 20 nm in length, causing dynein to stand up to 50 nm high \cite{Burgess2003}.

@@

Dynein's ability to step is entirely ATP driven under the process of ATP hydrolysis \cite{manna2020mechanistic, elshenawy2020lis1}. The ATP binds onto the motor domain and converts chemical energy into mechanical energy for dynein to transition between different conformational states (physicial arrangements) during a step. This process allows the binding domains to unbind and reattach at different locations on the microtubule and thus, permit varying step sizes. To measure dynein's step, an axis is defined on the microtubule.

@@

While ATP hydrolysis dictates the forward stepping during dynein's walk, the geometry of the domains is still a question for experimentalists. How exactly do the motor, tail, and linker achieve processive motion? Do the motor domains act as knees and stretch out for a step? Or do the knees stay bent, while the tail swings forward? Despite ongoing debates, recent studies suggest the former and named this process the powerestroke model \cite{Burgess2003}.

@@

Here, affinity refers to the tendency and strength of the domain binding to the microtubule - high affinity being a secure attachment to the microtubule, while low affinity is more relaxed. The cycle utilizes the conformational transitions between high and low affinity to explain dynein's unbinding and rebinding process. This transition is governed by the addition of an ATP unit, which loosens the ``foot" from the microtubule (steps 3 to 4), stretches the linker (steps 5 to 6), and tightens the ``foot" back onto the microtubule (steps 6 to 7), pulling the whole protein forward. This key detail within the transition of stretching the linker distinguishes a ``pre-" and a ``post-" stroke state during the powerstroke model and can be analogous to bending a knee upwards and kicking the foot forwards to stretch the knee and take a step. A closer visualization of the powerstroke and the transition between pre- and post-stroke states can be seen in Figure (\ref{fig:Powerstroke}), where the linker is highlighted in yellow.

@@

Experimentalists measures dynein in various ways that utilizes electron microscopy or quantum measuring devices. Some use optical tweezers to track dynein's motor domains, while others replace the tail with an artificial quantum rod \cite{kinoshita2018step, Dewitt2012}. Despite the different procedures, all measuring techniques suffer from their inability to measure steps within $\sim 0.4$ nm of where the binding domain lifted off. This causes short step lengths, where the binding domain quickly rebinds after unbinding, to be undetectable. The various measuring procedures and experimental limitations leads to different results and unique findings when observing different variables. In this paper, we focus on the unique observation by Yildiz \textit{et al.} of a stepping correlation between the initial interhead separation and step length because of the results contradicting previously accepted theories of independent stepping \cite{Dewitt2012}.

@@

Due to dynein's large size and stochastic nature, dynein's step was previously hypothesized to be independent from the initial conformational before the step \cite{wang1995single}. However, in 2012, Yildiz \textit{et al.} observed a correlation between the initial on-axis separation and the step length, indicating a dependence on the interhead separation \cite{Dewitt2012}. This discovery challenged established views on dynein's stepping processivity and pose the question of whether there exists interhead coordination between the motor domains when stepping. Figure (\ref{fig:YildizCorrelation}) below displays this correlation with a linear regression, where an existing non-zero slope indicates a dependence between the step and the initial on-axis separation.

@@

We want to further investigate Yildiz's unique stepping correlation by creating a compuational simulation of dynein and analyze the specific conditions that are required to replicate their results. Currently, other simulations that model dynein's step exist, but all of them are used to investigate the ATP hydrolysis mechanism during the mechanochemical cycle. These simulations suffer from numerous assumptions made about the physical aspects of dynein's step. Some assume that dynein can step only in increments of 8nm or that the rebinding process is constrained to a certain time frame \cite{singh2005monte, trott2018mathematical}. These limitations make it impossible for their models to replicate mechanical phenomenon observed in dynein's stepping, such as Yildiz's correlation from above.

To bridge this gap, Roundy \textit{et al.} constructed a physical model of dynein that explores the molecular interactions between the domains of dynein and its aqueous environment \cite{Capek2017, waczak2019drunken}. Instead of making assumptions about the physical mechanics of the step, Roundy's model neglects the chemistry of the ATP exchange and assumes the energy transfer from ATP is incorporated within the binding processes. Researchers John Waczak and Elliott Capek successfully incorporated this model under an angle-dependent Brownian dynamics simulation, where each domain experienced Brownian motion to mimic stochastic movement \cite{Capek2017, }. They were able to track dynein's precise movement along a walk and compare their stepping results to experiment. However, they also discovered that dynein spends less than 5\% of its total stepping time in the low affinity state where the dynein exhibits the actual stepping motion ($<1$ ms unbound while $>20$ ms bound). Because of this, their simulation suffered from immense computation time and lacked the ability to optimize model parameters for a better fit to experiment. For this work, we will use their simulation as a foundation but replace the dynamical bounded state with a Monte Carlo algorithm. This allows us to only simulate the stepping motion, as the Monte Carlo will initially test equilibrium configurations before the step. This new method will drastically shorten computation time and generate larger ensembles of statistics. We intend to use this model to reproduce experimental measures and help verify existing understandings concerning the properties of dynein’s stepping mechanism. More specifically, we want reproduce Yildiz's unique findings and investigate the stepping dependence on the interhead separation.

### 2021-05-05 papers/jin-thesis/Chapters/2Theory.tex
Thesis edits

\subsection{Two-State System}
According to the mechanochemical cycle (Figure \ref{fig:MechanochemicalCycle}), dynein can be in eight states over the course of a single step. However, many of these states possess similar conformations, where the dynein either has low affinity (unbinded domain diffusing above microtubule) or high affinity. Since we assume simple ATP exchange and that the two physical states are during binding and unbinding \cite{}, we categorize the cycle into two main conformations: the pre-stroke one-bound state and the post-stroke both-bound state.

@@

The key difference between the works in \cite{Capek2017, } (\textit{Elliott and John's paper}) and this paper is the implementation of a Monte Carlo algorithm in replacement for the Brownian dynamics both-bound state. In addition to the large both-bound time mentioned earlier, they noticed that the initial both-bound configuration of the motor and tail domains do not impact the stepping, giving a better incentive to apply a Monte Carlo approach. This new method of analyzing the both-bound state will significantly improve computational efficiency while still maintaining the dynamical simulation of the actual step in the one-bound state.

@@

The final force is the tension force, \textbf{F}$_T$, between the domains \textit{via} their connecting rods. Incorporting all these forces, we produce the \textit{Langevin Equation}:
\begin{equation}
	-\gamma \dot{\textbf{r}} + \textbf{F}_{rand} + \textbf{F}_T = m\ddot{\textbf{r}}.
\end{equation}
To properly demonstrate Brownian dynamics, we must assume strong drag where $|\gamma \dot{\textbf{r}}|\ll |m\ddot{\textbf{r}}|$. In other words, we assume that the immense viscosity in the environment restricts the ability for the domains to accelerate. Simplifying the \textit{Langevin Equation} and solving for $\dot{\textbf{r}}$, we get:
\begin{equation}
	\dot{\textbf{r}}=\frac{1}{\gamma}(\textbf{F}_{rand} + \textbf{F}_T)
\end{equation}
which is a differential equation we can solve for the equations of motion for the domains in the one-bound state. The derivation and final equations of motion can be found in \cite{Capek2017, W}

\subsection{Monte Carlo for Both-Bound}
Since dynein spends most of its stepping time in the both-bound state, we safely assume dynein equilibriates before unbinding. This allows us to use Monte Carlo methods for analyzing dynein's step by interpreting our model as a system. Typically, Monte Carlo methods analyze equilibrium theromodynamics of fluids, where a system of atoms possess many different microstates. For this model, dynein is the system and the many possible both-bound configurations are the ``microstates." However, unlike the more commonly known Markov Chain Monte Carlo, each both-bound configuration is independent and can generate different total energy values. This produces a large ensemble of of both-bound configurations, which we sample to create stepping statistics. Eventually, these statistics will reduce to probability distributions for important variables.

>>>>

\subsection{Two-State System}
According to the mechanochemical cycle (Figure \ref{fig:MechanochemicalCycle}), dynein can be in eight states over the course of a single step. However, many of these states possess similar conformations, where the dynein either has low affinity (unbinded domain diffusing above microtubule) or high affinity. Since we assume simple ATP exchange and that the two physical states are during binding and unbinding, we categorize the cycle into two main conformations: the pre-stroke one-bound state and the post-stroke both-bound state.

@@

The key difference between the works in \cite{Capek2017, waczak2019drunken} and this paper is the implementation of a Monte Carlo algorithm in replacement for the Brownian dynamics both-bound state. In addition to the large both-bound time mentioned earlier, they noticed that the initial both-bound configuration of the motor and tail domains do not impact the stepping, giving a better incentive to apply a Monte Carlo approach. This new method of analyzing the both-bound state will significantly improve computational efficiency while still maintaining the dynamical simulation of the actual step in the one-bound state.

@@

The final force is the tension force, \textbf{F}$_T$, between the domains \textit{via} their connecting rods. Incorporting all these forces, we produce the \textit{Langevin Equation}:
\begin{equation}
	-\gamma \dot{\textbf{r}} + \textbf{F}_{rand} + \textbf{F}_T = m\ddot{\textbf{r}}.
\end{equation}
To properly demonstrate Brownian dynamics, we must assume strong drag where $|\gamma \dot{\textbf{r}}|\ll |m\ddot{\textbf{r}}|$. In other words, we assume that the immense viscosity in the environment restricts the ability for the domains to accelerate. Simplifying the \textit{Langevin Equation} and solving for $\dot{\textbf{r}}$, we get:
\begin{equation}
	\dot{\textbf{r}}=\frac{1}{\gamma}(\textbf{F}_{rand} + \textbf{F}_T)
\end{equation}
which is a differential equation we can solve for the equations of motion for the domains in the one-bound state. The derivation and final equations of motion can be found in \cite{Capek2017}

\subsection{Monte Carlo for Both-Bound}
Since dynein spends most of its stepping time in the both-bound state, we safely assume dynein equilibriates before unbinding. This allows us to use Monte Carlo methods for analyzing dynein's step by interpreting our model as a system. Typically, Monte Carlo methods analyze equilibrium theromodynamics of fluids, where a system of atoms possess many different microstates \cite{lim2007vorticity}. For this model, dynein is the system and the many possible both-bound configurations are the ``microstates." However, unlike the more commonly known Markov Chain Monte Carlo, each both-bound configuration is independent and can generate different total energy values. This produces a large ensemble of of both-bound configurations, which we sample to create stepping statistics. Eventually, these statistics will reduce to probability distributions for important variables.

### 2021-05-05 papers/jin-thesis/Chapters/3Methods.tex
Thesis edits

	\item Calculate the distance between the binding domains and check if the distance is within a range of $L\pm l$, where $l$ is arbitrarily small. If not, repeat step 2.
	   \davidsays{Mention going back to 2 if the distance isn't in range.}
\end{enumerate}

@@

A more in-depth explanation and rigorous flow chart for the one-bound Brownian dynamics simulation can be found here \cite{Capek2017, }.

@@

Despite simulating many combinations of parameters, the number of free variables still produce many degrees of freedom. This makes it difficult to test the entire parameter space and truly invesitage the relationships between different sets of parameters. We approach this problem by individually attributing the parameters to a specific data set from exerpiment. For instance, the exponential unbinding constant, $C$, is fitted specifically to Figure (\ref{fig:trailingbias}). We use time data (\textit{cite paper for time data}\cite{}) to fit the unbinding rate constant, $k_{ub}$, because the inverse yields the average time it takes to unbind, i.e. the both-bound time. The rebinding rates, $k_a$ and $k_b$, are harder to optimize because they directly correlate to step length. The ability for dynein to take long steps is dependent on how long dynein diffuses above the microtubule. Therefore, the rebinding rates have a much larger parameter space due to the flexibility of optimizing according to the one-bound time or step length. Since we are interested in Yildiz's step lengths, we match these rates to the linear regression from Figure (\ref{fig:YildizCorrelation}) and Yildiz's step length plots. The last parameters are the spring constants. The spring constants also influence the step length because they dictate the strength of the restoring force. We fit the spring constants last to control the variance of step lengths.

>>>>

	\item Calculate the distance between the binding domains and check if the distance is within a range of $L\pm l$, where $l$ is arbitrarily small. If not, repeat step 2.
\end{enumerate}

@@

A more in-depth explanation and rigorous flow chart for the one-bound Brownian dynamics simulation can be found here \cite{waczak2019drunken}.

@@

Despite simulating many combinations of parameters, the number of free variables still produce many degrees of freedom. This makes it difficult to test the entire parameter space and truly invesitage the relationships between different sets of parameters. We approach this problem by individually attributing the parameters to a specific data set from exerpiment. For instance, the exponential unbinding constant, $C$, is fitted specifically to Figure (\ref{fig:trailingbias}). We fit the unbinding rate constant, $k_{ub}$, according to velocities for dynein's walk by matching to experimental trajectory data. The rebinding rates, $k_a$ and $k_b$, are harder to optimize because they directly correlate to step length. The ability for dynein to take long steps is dependent on how long dynein diffuses above the microtubule. Therefore, the rebinding rates have a much larger parameter space due to the flexibility of optimizing according to the one-bound time or step length. Since we are interested in Yildiz's step lengths, we match these rates to the linear regression from Figure (\ref{fig:YildizCorrelation}) and Yildiz's step length plots. The last parameters are the spring constants. The spring constants also influence the step length because they dictate the strength of the restoring force. We fit the spring constants last to control the variance of step lengths.

### 2021-05-05 papers/jin-thesis/Chapters/4Results.tex
Thesis edits

\begin{table}[H]
  \centering
  \begin{tabular}{|l | r | r | r|}
  	\hline
    Param & Model & Experimental & Source \\
    \hline
    $c_b$ & $\cb \Delta G_{ATP}$ &  & \\
    $c_m$ & $\cm \Delta G_{ATP}$ &  & \\
    $c_t$ & $\ct \Delta G_{ATP}$ &  & \\
    $k_a$ & $\kstk s^{-1}$&  & \\
    $k_b$ & $\kb s^{-1}$&  & \\
    $k_{ub}$ & $\kub s^{-1}$ & & \\
    $C$ & $\cexp$ & & \\
    $L_s$ & $\ls nm$ & $21nm$ & \cite{Burgess2003, 3vkh-cite, carter-paper}\\
    $L_t$ & $\lt nm$ & $23nm$ & \cite{Burgess2003, 3vkh-cite, carter-paper}\\
    $\theta_b$ & $\eqb$ &  120 & \cite{leschziner} \\
    $\theta_m^{\mbox{pre}}$ & $\eqmpre$ &  197 & \cite{Burgess2003}\\
    $\theta_m^{\mbox{post}}$ & $\eqmpost$ & 242 & \cite{Burgess2003}\\
    $\theta_t$ & $\eqt$ &  & \\
    $R_t$ & $\radiust nm$ & $4nm$ & \cite{Burgess2003}\\
    $R_m$ & $\radiusm nm$ & $5.5nm$ & \cite{Burgess2003}\\
    $R_b$ & $\radiusb nm$ & $1.25nm$ & \cite{Burgess2003}\\
    \hline
  \end{tabular}
  \caption{Optimized model parameters for Figures (\ref{fig:DataFitYildiz}-\ref{fig:Trajectory}).}
  \label{tab:params}
\end{table}

@@

The bottom plot in Figure (\ref{fig:DataFitYildiz}) displays the one-dimensional probability density of step lengths, defined as final displacement ($x_f$) minus initial displacement ($x_i$). The accumulative density from the diagonal shaded region is evident in this plot due to the peak at 0 nm. However, experiment was unable to detect 0 nm steps and is shown from the dip in Experiment Fig 3A (small density at 0 nm were lateral steps on the off-axis with little change on the on-axis). Our model suggests that dynein can still achieve forward directed motion with more positive steps than negatives ones but prefers short stuttered steps with fast one-bound times. A distribution of said one-bound times is shown below in Figure (\ref{fig:OBtime})

@@

As the distribution of times in Figure (\ref{fig:OBtime}) indicates, the model dynein frequently spends $<$ 0.1 $\mu s$ in the one-bound state, with the dynein most likely to rebind immediately after the affinity transitions. This demonstrates the importance of a buffer time when the dynein unbinds to avoid instantaneous rebinding while still achieving large positive step lengths. A deeper analysis of this will be discussed in the Limiting Cases section (Section \ref{sec:LimitingCase}).

@@

Based on the resemblence with experimental observations, we are fairly confident with the model's ability to replicate the stepping patterns of real dynein. In our spring model, we assumed each domain to act as springs to influence the powerstroke. However, the simulations displayed more consistent forward stepping when we turned off the binding domain spring and only allowed the motor and tail to have non-zero spring constants. That is, $c_b=0$ while $c_m=c_t=1$ from Table (\ref{tab:params}). This adjustment displays the flexibility within the model and the potential to fine-tune paramters to fit different sets of data.

\newpage
\section{Limiting Case}\label{sec:LimitingCase}

As mentioned previously, the model dynein had to take very rapid steps in order to closely generate Yildiz's stepping correlation. To lessen the error and achieve a slope closer to Yildiz's value of 0.6, the binding rate ($k_b$) and affinity transition rate ($k_a$) must both increase significantly. This led to instantaneous rebinding, as we investigated the limiting case of $k_a\gg k_b$ (affinity transition time $t_a\to 0$) and is shown in Figure (\ref{fig:DataFitYildiz99})

@@

When fitting to Yildiz's slope, we avoided instant rebinding by also prioritizing the large positive step lengths Yildiz observed in Experiment Fig 3A (on Figure \ref{fig:DataFitYildiz}). The binding and affinity transition rates can be better optimizied to fit the larger step lengths (we classified ``large'' steps as $> 40$ nm), but doing so would decrease the correlation between the displacements and thus, the value for the slope. This caused an optimization problem of whether to fit according to the slope or the step lengths. We believed that the parameters shown in Table (\ref{tab:params}) best demonstrated the functionality of the displacements from the slope, while maintaining dynein's forward directionality with a similar step length trend towards large steps.

>>>>

\begin{table}[H]
  \centering
  \begin{tabular}{|l | r | r | r|}
  	\hline
    Param & Model & Experimental & Source \\
    \hline
    $c_b$ & $\cb \Delta G_{ATP}$ &  & \\
    $c_m$ & $\cm \Delta G_{ATP}$ &  & \\
    $c_t$ & $\ct \Delta G_{ATP}$ &  & \\
    $k_a$ & $\kstk s^{-1}$&  & \\
    $k_b$ & $\kb s^{-1}$&  & \\
    $k_{ub}$ & $\kub s^{-1}$ & & \\
    $C$ & $\cexp$ & & \\
    $L_s$ & $\ls nm$ & $21nm$ & \cite{Burgess2003, 3vkh-cite, carter-paper}\\
    $L_t$ & $\lt nm$ & $23nm$ & \cite{Burgess2003, 3vkh-cite, carter-paper}\\
    $\theta_b$ & $\eqb$ &  120 & \cite{leschziner} \\
    $\theta_m^{\mbox{pre}}$ & $\eqmpre$ &  197 & \cite{Burgess2003}\\
    $\theta_m^{\mbox{post}}$ & $\eqmpost$ & 242 & \cite{Burgess2003}\\
    $\theta_t$ & $\eqt$ &  & \\
    $R_t$ & $\radiust nm$ & $4nm$ & \cite{Burgess2003}\\
    $R_m$ & $\radiusm nm$ & $5.5nm$ & \cite{Burgess2003}\\
    $R_b$ & $\radiusb nm$ & $1.25nm$ & \cite{Burgess2003}\\
    \hline
  \end{tabular}
  \caption{Optimized model parameters for Figures (\ref{fig:DataFitYildiz}-\ref{fig:BBPlots}).}
  \label{tab:params}
\end{table}

@@

The bottom plot in Figure (\ref{fig:DataFitYildiz}) displays the one-dimensional probability density of step lengths, defined as final displacement ($x_f$) minus initial displacement ($x_i$). The accumulative density from the diagonal shaded region is evident in this plot due to the peak at 0 nm. However, experiment was unable to detect 0 nm steps. This was shown from the dip in Experiment Fig 3A, where the small density at 0 nm were lateral steps in the off-axis. Figure (\ref{fig:DataFitYildiz}) suggests that dynein can still achieve forward directed motion from favoring positive steps rather than negative ones, but prefers short stuttered steps with fast one-bound times. A distribution of said one-bound times is shown below in Figure (\ref{fig:OBtime})

@@

As the distribution of times in Figure (\ref{fig:OBtime}) indicates, the model dynein frequently spends $<$ 0.1 $\mu s$ in the one-bound state, with the dynein most likely to rebind immediately after the affinity transitions. This demonstrates the importance of a buffer time when the dynein unbinds to avoid instantaneous rebinding while still achieving large positive step lengths. A deeper analysis of this will be discussed in the Limiting Cases section (Section \ref{sec:LimitingCases}).

@@

Based on the resemblence with experimental observations, we are fairly confident with the model's ability to replicate the stepping patterns of real dynein. In our spring model, we assumed each domain to act as springs to influence the powerstroke. However, the simulations displayed more consistent forward stepping when we ``turned off" the binding domain spring and only allowed the motor and tail to have non-zero spring constants. That is, $c_b=0$ while $c_m=c_t=1$ from Table (\ref{tab:params}). This adjustment displays the flexibility within the model and the potential to fine-tune paramters to fit different sets of data.

\newpage
\section{Limiting Cases}\label{sec:LimitingCases}

As mentioned previously, the model dynein took very rapid steps in order to closely generate Yildiz's stepping correlation. To lessen the error and achieve a slope closer to Yildiz's value, dynein would have to take even faster steps. We investigated this by increasing the affinity transition rate ($k_a$) significantly, which nullified the buffer period after unbinding. This limiting case of $k_a\gg k_b$ (affinity transition time $t_a\to 0$) is shown in Figure (\ref{fig:DataFitYildiz99})

@@

As Figure (\ref{fig:DataFitYildiz99}) showed, dynein exhibited instantaneous rebinding. If we ignored the transition period between low and high affinity, the model dynein would immediately rebind with an average one-bound time of 5 ns. The step length plot in Figure (\ref{fig:DataFitYildiz99}) also displayed a lack of directionality when stepping.

We avoided instant rebinding by also prioritizing the large positive step lengths Yildiz observed in Experiment Fig 3A (we classifed ``large'' steps as $> 40$ nm). By lowering the binding and affinity transition rates,  the model dynein recorded larger step lengths better and achieved processive motion. However, decreasing the rates would subsequently decrease the correlation between the displacements and thus, the value for the slope. This caused an optimization problem of whether to fit according to the slope or the large step lengths. We believed that the parameters shown in Table (\ref{tab:params}) best demonstrated the functionality of the displacements from the slope, while maintaining dynein's forward directionality with a similar step length trend towards large steps.

### 2021-05-05 papers/jin-thesis/Chapters/5Conclusion.tex
Thesis edits

We successfully incorporated a Monte Carlo algorithm when dynamically simulating dynein's unique stepping mechanism. By modelling dynein as a two-dimensional particle-rod system, we separated the conformations of the mechanochemical cycle into a both-bound and one-bound state and emulated the powerstroke with springs in each domain. With various degrees of freedom controlling the properties of a step, the model was able to flexibly optimize according to experimental results and provide further conclusions for observations. More specifically, we replicated experimentalist Ahmet Yildiz's unique result of an observered stepping correlation between the initial domain separation and final displacement with a 16.5\% error.

>>>>

We successfully incorporated a Monte Carlo algorithm when dynamically simulating dynein's unique stepping mechanism. By modelling dynein as a two-dimensional particle-rod system, we separated the conformations of the mechanochemical cycle into a both-bound and one-bound state and emulated the powerstroke with springs in each domain. With various degrees of freedom controlling the properties of a step, the model was able to flexibly optimize according to experimental results and provide further conclusions for correlated stepping. More specifically, we replicated experimentalist Ahmet Yildiz's unique result of an observered stepping correlation between the initial domain separation and final displacement with a 16.5\% error.

### 2021-05-05 papers/jin-thesis/main.tex
Thesis edits

\newpage
\cite{Burgess2003} \cite{Cianfrocco2015mechanism} \cite{Dewitt2012} \cite{Capek2017, waczak2019drunken}
\cite{GoodsellArt} \cite{eschbach2011cytoplasmic}
\cite{rao2019molecular} \cite{manna2020mechanistic} \cite{desantis2017lis1} 
\cite{elshenawy2020lis1} \cite{ando2020small} \cite{kinoshita2018step} \cite{qiu2012dynein} \cite{muller1973dynamic} \cite{lim2007vorticity} \cite{fehr2008kinesin} \cite{trott2018mathematical}

\bibliographystyle{unsrt}
\bibliography{references}

>>>>

\newpage

\bibliographystyle{plain}
\bibliography{references}
